### 2013-02-28 doc/final_report/testing.tex
Created files for chapters of diss
Added final report stuff

%%------------------------------------------------------
%  
%  Implementation include for dissertation
%
%------------------------------------------------------

\subsection{ Data Mining \& Paper Processing}

\subsection{ Web Interface \& Database System}

\subsection{ Paper Type Classification }

>>>>

%%------------------------------------------------------
%  
%  Testing include for dissertation
%
%------------------------------------------------------

\subsection{ Unit Testing }

\subsection{ User Testing }

Once a basic user interface had been implemented, the system was opened for
user testing. The main Patridge instance
(\url{http://farnsworth.papro.org.uk/}) was advertised using several social
media streams and users encouraged to submit bug reports if they experienced
any problems whilst using the site.

\subsection{ Testing Learning Algorithms }

Patridge uses machine learning algorithms to classify the type of research
papers added to its database. It was therefore necessary to test that these
algorithms were sufficiently trained and provide accurate classification.
Unlike
